\documentclass[12pt,english]{scrartcl}

\usepackage{amsmath,amssymb}
%\usepackage[amssymb]{SIunits}
\usepackage{babel}
\usepackage[latin1]{inputenc}
\usepackage{graphicx}
\usepackage{color}

\title{KOGW-PM-KNP: Tutorial 2 - G{\"u}nt{\"u}rk{\"u}n`s Magpies}
\author{}
\date{\today}

\begin{document}

\maketitle

Working in a pairs, read the paper by Prior, Schwarz and G{\"u}nt{\"u}rk{\"u}n (2008) and answer the following questions:
\begin{enumerate}
 \item What was the research question the authors wanted to address? [1] \\
 \color{blue}
 Any 1 from below:
 \begin{itemize}
 \item Do magpies have self-awareness?
 \item Does a sense of self, characterised by social intelligence, follow convergent
evolution?
 \item Is a laminated cortex a prerequisite for self-recognition?
 \end{itemize}
 
 \color{black}
 \item What experimental hypothesis did they formulate in order to test their research questions? Try to express this hypothesis in ``IF ..., then ...'' form. [2] \\
 \color{blue}
 \begin{itemize}
 \item IF magpies exhibit self-directed behaviour, i.e. attempt to remove the mark
from their bodies,
 \item THEN they exhibit self-recognition.
 \end{itemize}
 
 \color{black}
 \item Identify the independent and dependent variables in the experiment. [5]\\
 \color{blue}
 Independent (any 3)
 \begin{itemize}
  \item Identity of birds (Gerti, Goldie, etc.)
  \item Color of marks
  \item Presence of mirror
  \item Size of cage cell (1 or 2 compartments)
  \end{itemize}
 Dependent
 \begin{itemize}
 \item Contingency behaviour (self-recognition) vs conspecific behaviour (aggressive,
social, etc.)
 \item Quantity of self directed behaviour (behavioural activity directed towards the
marked region)
 \end{itemize}
 
 \color{black}
 \item What type of realizations/operationalizations did the authors use to observe the dependent variable? [4] \\
 \color{blue}
 Any 4:
 \begin{itemize}
  \item Measure time spent in mirrored vs unmirrored compartments.
  \item Number of close inspections of the mirror.
  \item Looks behind the mirror.
  \item Contingent vs Social behaviour.
  \item Frequency of spontaneous self-directed (mark-directed) behaviour
 \end{itemize}
 
 \color{black}
 \item What variables did the authors identify as potentially confounding factors and how did they control for them? [2] \\
 \color{blue}
 Any 2:
 \begin{itemize}
  \item Exhibit self-directed behaviour without a mirror -¿ introduce a non-reflective
sheet in place of the mirror in control trials
  \item Exhibit self-directed behaviour without seeing the mark -¿ introduce a black
(sham) mark
  \item Operant conditioning - use small number of trials so the birds don't become
conditioned to the experimental setup and produce biased results.
  \item Handling - bird's eyes are shielded from seeing the mark being applied to
their bodies.
  \item Influenced by colour of mark - introduce 3 different colours as well as sham.
  \item General increase in behavioural activity may result in more instances of ap-
parent self-directed behaviour - measure quantity of behavioural activity in
various trials.
 \end{itemize}
 
 \color{black}
 \item What other potential confounds could you think of that the authors did not control and that could potentially invalidate their research? [2] \\
 \color{blue}
 Any 2:
 \begin{itemize}
  \item Social upbringing of the birds (Hand raised vs Wild ("anatural social conditioning").
  \item Experimenters subjective rulings of displayed behaviours.
  \item Validation through comparison to other study that could potentially be flawed
(a.k.a. Ape studies)
  \item Too small sample size to be definitive for a population
  \item Mark could be within magpies visual field.
 \end{itemize}
 
 \color{black}
 \item Label the design as within- or between group design. [2] \\
 \color{blue}
  Within-group design
 
 \color{black}
 \item Create an example design matrix, for one subject, that is, a matrix containing one row for each trial of the experiment, and one column each for the independent variable, the control variables and the trial number. [2] \\
 \color{blue}
 TBC.
 
 \end{enumerate}


Please email me your answers (marianne.maertens@tu-berlin.de), together with a text file containing your design matrix including column names. Don't forget to include the names of both partners. \\
Maximum marks 20/20

\end{document}